DOM Review Summary

### 2024-03-18 Analysis/ReviewSummary/ReviewSummary.qmd
Number of occasions
Number of primary, secondary, and total occasions plot

>>>>

```{r DataCollection_PrimaryOccasions}
#| echo: false

dataCollection_clean |>
  rowwise() |>
  mutate(Primary_Max = case_when(Primary_Max > 30 ~ 30,
                                  .default = Primary_Max)) |>

  ggplot() +
  geom_histogram(aes(x = Primary_Max),
                 binwidth = 1, fill = "darkslategrey") +
  labs(title = "Number of primary occasions",
       x = "Number of primary occasions", y = "Number of articles") +
  scale_x_continuous(breaks = c(1, 5, 10, 20, 30),
                     labels = c("1", "5", "10", "20", "30+"))
```

```{r DataCollection_SecondaryOccasions}
#| echo: false

dataCollection_clean |>
  filter(!is.na(Secondary_Max)) |>
  rowwise() |>
  mutate(Secondary_Max = case_when(Secondary_Max > 20 ~ 20,
                                   .default = Secondary_Max)) |>

  ggplot() +
  geom_histogram(aes(x = Secondary_Max),
                 binwidth = 1, fill = "darkcyan") +
  labs(title = "Number of secondary occasions",
       subtitle = "Where variable, maximum number of occasions is presented",
       x = "Number of secondary occasions", y = "Number of articles") +
  scale_x_continuous(breaks = c(1, 5, 10, 20),
                     labels = c("1", "5", "10", "20+"))
```

```{r DataCollection_TotalOccasions}
#| echo: false

dataCollection_clean |>
  filter(!is.na(Secondary_Max) & !is.na(Primary_Max)) |>
  mutate(TotalOccasions = Secondary_Max*Primary_Max) |>
  ggplot() +
  geom_histogram(aes(x = TotalOccasions),
                 binwidth = 0.1,
                 fill = "darkorchid3") +
  labs(title = "Total number of occasions",
       subtitle = "Product of primary and secondary occasions",
       x = "Number of occasions (log10 scale)", y = "Number of articles") +
  scale_x_continuous(transform = "log10",
                     breaks = c(4, 10, 25, 50, 100, 500, 1000, 2000)) +
  scale_y_continuous(breaks = c(1, 3, 6, 9))
```
